---
  title: "Statistical Inference Course Project"
  author: "LPT"
  date: "Tuesday, Jan 20, 2014"
---
  
## Synopsis:
In this project you will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations. You will investigate the distribution of averages of 40 exponentials. Note that you will need to do a thousand simulations.

```{r knitr_options, include=FALSE, echo=TRUE}
library(knitr)
opts_chunk$set(fig.width=12, fig.height=4, fig.path='RmdFigs/',
               warning=FALSE, message=FALSE)
```

##Simulations
```{r Simulations, cache=TRUE}
set.seed(800)
lambda <- 0.2

# to investigate 40 samples based on 1000 simulations
nSam <- 40
nSim <- 1:1000

# average of 40 samples
Means <- data.frame(x = sapply(nSim, function(x) {
    mean(rexp(nSam, lambda))
}))

```

##Question 1
Mean of 40 samples is:
  
```{r Results1}
mean(Means$x) 
```

Theoretical mean (1/lambda) is:
```{r TResults1}
1/lambda   
```
1. The above results shows that the center of distribution of averages of 40 samples is close to the theoretical center of the distribution.


##Question 2
Variance of 40 samples is:
```{r Results2}
var(Means$x)    
```

Theoretical variance is:
```{r TResults2}
((1/lambda)/sqrt(nSam))^2   
```
2. The above results shows that the computed variance is close to the theoretical variance of the distribution.

##Question 3
```{r Results3}
library(ggplot2)
ggplot(data = Means, aes(x = x)) + geom_histogram(aes(y = ..density..), fill = I("pink"), 
    binwidth = 0.2, color = I("blue")) + stat_function(fun = dnorm, arg = list(mean = 5, 
    sd = sd(Means$x)))

```
3. The plot shows that the distribution is approximately normal.